---
title: "lab-07-simpsons.Rmd"
author: wejdan awad.
date: "17 March 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r load_libraries, message=FALSE}
library(tidyverse) 
library(mosaicData)
```


## Exercises


1.  
```{r whickam}
?Whickham
```
    
Your answer:
Observational ,because we just watching the people and write the notes also we didn't involving in any situation or controlling any variables.
2.  
```{r observations}
nrow(Whickham)
```

Your answer;
1314, represent recorded participants age, smoking status at baseline 
3.  

```{r number_variables}
 ncol(Whickham)
```

Your answer:  
3, age (Numerical), smoker and outcome are categorical 
age (anteger), smoker and outcome are  (factor),
```{r var_type}
class(Whickham$age)
class(Whickham$smoker)
class(Whickham$outcome)
```

Your answer: 
age (Numerical) ,smoker and outcome are categorical 
age (integer) , smoker and outcome are (factor)

```{r plot_outcome}
ggplot(Whickham, aes(x=outcome)) + geom_bar()
```


```{r plot_smoker}
ggplot(Whickham, aes(x=smoker)) + geom_bar()
```

```{r plot_age}
ggplot(Whickham, aes(x=age)) + geom_bar()
```


4. 
I expect the health will be worser and may be the person will be died after while, if he keeping smoke 
```{r plot_smokeVSincome_1}
ggplot(data=Whickham, aes(x=smoker, y=outcome , color=outcome)) + geom_bar(stat="identity" )
```

Knit, commit, and push to github.

5. 

```{r plot_smokeVSincome_2}
Whickham %>%
  count(smoker, outcome)
502+230
230/732
```
smoker(732) NO 31,4 (Dead) << (68.6)Alive 
smoker(582) yes 23,8 (Dead)<< (76.2)Alive 
i does not expected this result because now the most died people not smoker
6.

```{r age_cat}
 Whickham <- Whickham%>% mutate (age_cat = case_when (age <= 44 ~ "18-44", age > 44. & age <= 64 ~ "45-64", age > 64 ~ "65+"))
```

7. 

```{r plot_smokeVSincome_3}
ggplot(data=Whickham, aes(x=outcome, y=smoker,color=smoker, fill=age_cat)) + geom_bar(stat="identity") +facet_wrap(~age_cat)
```
what changes > the category of the age it's appear to us and we see the most of dead people not smoker in age ( 65+).. but in age ( 45-64) and (18-44) the most dead pepole are smoker that is relationship between the smoking and helath not clearly but that helath will be change to Morst if you be smoker

Knit, commit, and push to github.