---
title: "lab-07-simpsons.Rmd"
author: wejdan awad.
date: "17 March 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r load_libraries, message=FALSE}
library(tidyverse) 
library(mosaicData)
```


## Exercises


1.  
```{r whickam}
View(Whickham)
```
    
Your answer:
Observational ,because we just watching the people and write the notes also we didn't involving in any situation or controlling any variables.
2.  
```{r observations}
nrow(Whickham)
```

Your answer;
1314, represent recorded participants age, smoking status at baseline 
3.  

```{r number_variables}
 ncol(Whickham)
```

Your answer:  
3, age (Numerical), smoker and outcome are categorical 
age (anteger), smoker and outcome are  (factor),
```{r var_type}
class(Whickham$age)
class(Whickham$smoker)
class(Whickham$outcome)
```

Your answer: 
age (Numerical) ,smoker and outcome are categorical 
age (integer) , smoker and outcome are (factor)

```{r plot_outcome}
ggplot(Whickham, aes(x=outcome)) + geom_bar()
```


```{r plot_smoker}
ggplot(Whickham, aes(x=smoker)) + geom_bar()
```

```{r plot_age}
ggplot(Whickham, aes(x=age)) + geom_bar()
```


4. 
I expect the health will be worser and may be the person will be died after while, if he keeping smoke 
```{r plot_smokeVSincome_1}
ggplot(data=Whickham, aes(x=smoker, y=outcome , color=outcome)) + geom_bar(stat="identity" )
```

Knit, commit, and push to github.

5. 

```{r plot_smokeVSincome_2}
Whickham %>%
  count(smoker, outcome)
```

6.

```{r age_cat}

```

7. 

```{r plot_smokeVSincome_3}

```

Knit, commit, and push to github.